Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-02-25 phaseDelay.tex
Updates from ShareLaTeX

>>>>

\section{Background}

It is no understatement to say that 
concerns with  phase delay have 
a major  motivator for changing
SE practices. Basili and Boehm~\cite{boehm01}  commented in
2001 that, since the 1980s, the phase delay
``has been a major driver in focusing
industrial software practice on thorough
requirements analysis and design,
on early verification and validation, and
on up-front prototyping and simulation
to avoid costly downstream fixes.''

Also, concerns with the phase delay  had
 a significant impact on the history of agile programming. Kent Beck is
 particulary eloquent

Under certain circumstances, the exponential rise in the cost of changing software over time can be flattened. If we can flatten the curve, old assumptions about the best way to develop software no longer hold.

One of the universal assumptions of software engineering is that the cost of changing a program rises exponentially over time. I can remember sitting in a big linoleum-floored classroom as a college junior and seeing the professor draw on the board the curve found in Figure 1.

The cost to fix a problem in a piece of software rises exponentially over time. A problem that might take a dollar to fix if you found it during requirements analysis might costs thousands to fix once the software is in production."

I resolved then and there that I would never let a problem get through to production. No sirree, I was going to catch problems as soon as possible. I would work out every possible problem in advance. I would review and crosscheck my code. No way was I going to cost my employer $100,000.
